Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-21 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Add color to comparison MWR plot to show within 500 km

```{r echo = FALSE, fig.width = 4, fig.height = 3}
compare_rain %>% group_by(fips) %>%
        summarize(ave_rain_mm = mean(rain_mm),
                  ave_tot_precip = mean(tot_precip),
                  n = n()) %>%
        ggplot(aes(x = ave_tot_precip, y = ave_rain_mm, size = n)) + 
        geom_point(alpha = 0.5) + 
        theme_bw() +
        xlim(c(10, 225)) + ylim(c(10, 225)) + 
        geom_abline(intercept = 0, slope = 1) + 
        xlab("Rainfall based on NLDAS-2 data (mm)") + 
        ylab("Rainfall reported in Monthly \nWeather Report (mm)")
```

>>>>

```{r echo = FALSE, fig.width = 4, fig.height = 3}
compare_rain %>% group_by(fips) %>%
        summarize(ave_rain_mm = mean(rain_mm),
                  ave_tot_precip = mean(tot_precip),
                  n = n(),
                  within_500_km = first(storm_dist) <= 500) %>%
        ggplot(aes(x = ave_tot_precip, y = ave_rain_mm, 
                   size = n, color = within_500_km)) + 
        geom_point(alpha = 0.5) + 
        theme_bw() +
        xlim(c(10, 225)) + ylim(c(10, 225)) + 
        geom_abline(intercept = 0, slope = 1) + 
        xlab("Rainfall based on NLDAS-2 data (mm)") + 
        ylab("Rainfall reported in Monthly \nWeather Report (mm)") + 
        scale_color_manual(values = c("blue", "black"), guide = "none") 
```
